\thispagestyle{plain}

\chapter*{Acknowledgements} 
%\vspace*{4cm}

I would like to express my gratitude to my thesis advisor Prof. Jan Lundgren of the Department of Computer and Electrical Engineering (DET). He consistently allowed this research to be my own work while steering me in the right direction whenever he thought I needed it. Also, I would like to specially thank Prof. Mattias O’Nils for his guidance and help and all my colleagues from DET for their support.

I am also very grateful to all my colleagues from the University of Salerno (UNISA), including Marco Carratù, Prof. Consolatina Liguori, Prof. Antonio Pietrosanto, Matteo Ferro, Avoci Ugwiri Moise et al. Prof. Paolo Sommella, especially deserves my thanks for his valuable feedback and guidance in my research over the past four years.


Finally, I must express my very profound gratitude to my family and all my friends for providing me with unfailing support and unstinting encouragement during my years of study and throughout the process of researching and writing this thesis. This accomplishment would not have been possible without their support. Especially my husband Yang Xie, during the years of studying in different places, he never left me, and encouraged me to move forward with warm love and support. Thank you!
% I would like to extend my sincere thanks to my supervisors Mattias O´Nils and Silvia Krug to guide, support and encourage me.
% I must also thank To Faisal.Z.Qureshi for his valuable help.

\vspace{0.5cm}
% Many thanks to Permobil for the cooperation.
% I owe a big thanks to the EU regional development funds and Mid Sweden University for funding my work, and I’d also like to extend my gratitude to all my colleagues from the electronics design department. It was great sharing time with all of you!
%\textarab{نص عربي }
%\RL{السَلامُ عَليكم ورَحمةُ الله وبَركاته}
%\setcode{utf8}
%\begin{RLtext} نص عربي \end{RLtext}
%\textarab{نص عربي }
%\RL{السَلامُ} عَليكم ورَحمةُ الله وبَركاته

%\arab{غ}